### 2020-01-27 wuhan.tex
more updates

\begin{figure}[t]
\includegraphics[width=\textwidth]{../fig/comparison.pdf}
\caption{
Early estimates of $\mathcal R_0$ and associated assumptions about $r$ and $g(\tau)$.
}
\end{figure}

@@

To assess the amount of uncertainties in the estimate of $\mathcal R_0$,
we come up with distributions that span over the assumptions made by other people:
\begin{equation}
\begin{aligned}
r &\sim \mathrm{Gamma}(\alpha=5, \beta=5/0.15)\\
\bar{G} &\sim \mathrm{Gamma}(\alpha=10, \beta=10/8.5)\\
\kappa &\sim \mathrm{Gamma}(\alpha=10, \beta=10/0.35)\\
\end{aligned}
\end{equation}
These give median estimate of $\mathcal R_0$ of 2.37 with 95\% qunatile of 1.26--9.01.

\begin{table}[!th]
\begin{center}
\begin{tabular}{l|c|c|c|c}
Study & $\mathcal R_0$ & $r$ ($\textrm{days}^{-1}$) & $\bar G$ (days) & $\kappa$ \\
\hline
\cite{imaincov} & 2.5 (1.5--3.5) & 0.14 (0.05--0.21) & 8.4 & unspecified$^\ast$ \\
\hline
\cite{majumderncov} & 2.0--3.3 & 0.07--0.20 & 6--10 & 0 \\
\hline
\cite{readncov} & 3.8 (3.6--4.0) & 0.25 (0.25--0.26)$^\dagger$ & 7.6 & 0.5 \\
\hline
\cite{riouncov} & 2.2 (1.4--3.8) & 0.09 (0.03--0.27) & 7--14 & 0.5\\
\hline
\cite{zhaoncov} & 5.47 (4.16--7.1)$^\ddagger$ & 0.25 (0.21--0.30) & 7.6--8.4 & 0.2
\end{tabular}
\end{center}
\caption{
\textbf{Parameter estimates and assumptions}
Exponential growth rate $r$ is calculated by using the following formula: $r = (\mathcal R_0^\kappa - 1)/(\kappa \bar{G})$.
$^\ast$We assume $\kappa = 0.5$ to calculate $r$.
$^\dagger$Exponential growth rate $r$ is calculated by using the exact formula for the SEIR model \citep{ma2014estimating}.
$^\ddagger$Assuming no increase in the reporting rate.
}
\end{table}

>>>>

\begin{figure}[t]
\includegraphics[width=\textwidth]{comparison.pdf}
\caption{
Early estimates of $\mathcal R_0$ and associated assumptions about $r$ and $g(\tau)$.
}
\end{figure}

@@

\begin{equation}
\begin{aligned}
\mathcal R_i &\sim \textrm{distrib}(\theta_i)\\
\bar G_i &\sim \textrm{distrib}(\theta_i)\\
\kappa &\sim \textrm{distrib}(\theta_i)\\
\end{aligned}
\end{equation}
